\hfill ~\\[-30mm] \phantom{h} \hfill\mbox{\small pre-print number if any?} \\[1cm] \vspace{13mm} \textbf{Precise predictions for same sign W-bosons scattering at the LHC}

### 2017-11-14 Draft/crosssection.tex
WHIZZARD numbers

 In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
an excellent agreement among the various tools, which confirms the fact
that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $X \pm 0.001$  \\ 
        {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
        {\sc PHANTOM}&  $X \pm 0.0004 $  \\
        {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
        {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
        {\sc Whizard}&  $X \pm 0.0004 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}

>>>>

 In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described above, and in Fig.~\ref{fig:wg1_mjj-llLO} we show the results
for the tagging-jet (left) and lepton-pair (right) invariant-mass distribution. In both case we show the absolute distributions in the main frame of the 
figures, while in the inset the ratio over {\sc VBFNLO} is displayed. For both observables we find 
an excellent agreement among the various tools, which confirms the fact
that contributions from $s-$channel diagrams as well as from non-resonant configurations are strongly suppressed in the fiducial region.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $X \pm 0.0002$ \\
        {\sc MG5\_aMC}&  $X \pm 0.001$  \\ 
        {\sc MoCaNLO+Recola}  &  $1.4347 \pm 0.0001$ \\
        {\sc PHANTOM}&  $X \pm 0.0004 $  \\
        {\sc POWHEG}  &  $1.44092 \pm 0.00009$ \\
        {\sc VBFNLO}  &  $1.43796 \pm 0.00005$ \\
        {\sc Whizard}&  $1.4363 \pm 0.0009 $
    \end{tabular}
    \caption{\label{tab:wg1_LOrates} Rates at LO accuracy within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.}
\end{table}
